Overrelaxed Sinkhorn--Knopp Algorithm for Regularized Optimal Transport

### 2017-11-26 PosterNIPS2017.tex
Allegement intro poster

			\item[] Yet, for small regularization $\epsilon$, the SK algorithm becomes extremely slow. To counter this, we propose a new algorithm that accelerates SK by \emph{overrelaxation}.
			This idea has been numerically shown to accelerate the algorithm, but with no proof of convergence.
			We ensure global convergence by choosing the overrelaxation parameters at each step of the algorithm so that a given Lyapunov function decreases.

>>>>

			\item[] To counter the slowing of SK for small $\epsilon$, we propose a new algorithm based on \emph{overrelaxation}.
			Global convergence is ensured by choosing the overrelaxation parameters at each step of the algorithm so that a given Lyapunov function decreases.
